\subsection{Requirements}
\begin{itemize}
\item Visual Studio 2010 \cite{bib:visualstudio}\\
The game uses XNA 4.0 so earlier versions of Visual Studio are not guaranteed to work this also requires the project to be converted.

\item XNA Game Studio 4 \cite{bib:xna}\\
The game is built on XNA Game Studio 4.0
\end{itemize}

\subsection{Compiling and Running the game}
1. Open the SmashBros.sln file located in the TDT4240-X2/SmashBros folder.\\
2. Right click the SmashBros Project in the Solution Explorer and press "Set as Startup Project".\\
3. Go to the menu and press Debug>Start Debugging, or press F5.\\
4. The project should compile and start the game.

\subsection{Gameplay}
The first screen you will see is the character selection screen. Here you can select your character by moving your pointer with the XBox control pad or the W, A, S, D keys for player 1 and the arrow keys for player 2. Player 1 select his or her character by pressing the V key, and player 2 by pressing the J key. After selecting your characters, start the game by pressing the Return key. The game then lets you choose a level, which is selected in the same way as the character. As before you press the Return key to continue. When the game starts you can move around with the XBox control pad, the W, A, S, D keys for player 1, and the arrow keys for player 2. You can attack using the V key for player 1 and the J key for player 2. The goal of the game is to knock the opposing player, or players, off the map. This is done by attacking them using the knockback effect to push them off the map. Hitting your opponent, or opponents, will increase the power of the knockback and further improve your ability to knock them off the map. When a player's character is knocked off the map, he will respawn after a few seconds, loosing a "life".
