The architecture description could be found in ArchitecturalDoc.pdf file. The implementation has some inconsistencies with the planed architecture, caused by several different reasons. This chapter lists them and tries to explain the developers view and logic behind those changes.
Model View Controller (MVC)
In the architectural description modifiability is one of the primal attributes for the architecture, and had lead to the choice of MVC. Through the implementation we can observe some inconsistencies with the MVC architectural pattern. The reasons for these inconsistencies are caused majorly by the use of FarseerPhysics COT in the project.
Development View and Control-Float
Control- float of the program has been changed to fit better with FarseerPhysics engine, and now is different from the sequence diagram presented by the Scenario View and Development View in the architectural description, because of the great damage from the architectural-drift.
Possible reasons for inconsistencies
As the development team worked with the XNA framework, there were difficulties fitting MVC into XNAs pipe and filter architecture. Though the Architecture document gave a possible solution for how to implement MVC inside a pipe and filter pipeline, the difficulties only got worse with FarseerPhysics engine, resulting into an architectural-drift. This could be avoided earlier in the process if the architects had more experience and understanding of XNA and used COTs. If the development view was more strict and detailed, so it could give more support to the developers, the possibility of an architectural-drift and erosion would be considerably lower, resulting in a much more consisting product.